\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-02-07 relational.tex
first

%\chapter{Relational Modeling for Falsification}
%\label{chap:rel}

@@

\input{figs/segtraj_rel_enriched.tex}

@@

\inclfig[width=0.75\textwidth]{vdp_cont_traces.png}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.75\textwidth]{vdp_abs.png}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=\textwidth]{vdp_disc_map.png}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.40\textwidth]{vdp_graph.png}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}

>>>>

\newcommand{\pwa}{\rho}
\newcommand{\map}{f}
\newcommand{\amap}{f}
\newcommand{\gm}{\scr{T}}
\newcommand{\guard}{g}
\newcommand{\ds}{\scr{D}}

\chapter{Relational Modeling for Falsification}
\label{chap:rel}

@@

\input{figs/relational/segtraj_rel_enriched.tex}

@@

\inclfig[width=0.75\textwidth]{relational/vdp_cont_traces.png}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}
\label{fig:vdp-cont}

\inclfig[width=0.75\textwidth]{relational/vdp_abs.png}{The discovered
abstraction $\scr{H}(0.1)$. Red cells are unsafe cells and green cells are
initial cells.}
\label{fig:vdp-abs}

\inclfig[width=\textwidth]{relational/vdp_disc_map.png}{Cells and
trajectory segments used by $1$-relational modeling.}
\label{fig:vdp-map}

\inclfig[width=0.40\textwidth]{relational/vdp_graph.png}{Enriched
graph $G^R$. The affine maps $f$ for the transition relations are show
in \tabref{vdp-pwa}.}
\label{fig:vdp-graph}
